|

### 2020-05-23 paper/Manuscript.Rmd
Fixed figure problem
Make synthetic a bit more flexible wrt classes

```{r, scholarbib, echo = FALSE}
knitr::include_graphics("scholar_bib.png")
```

@@

The second solution implemented in `worcs` is to share a synthetic dataset with similar characteristics to the real data. Synthetic data mimic the level of measurement and (conditional) distributions of the real data [see @nowokSynthpopBespokeCreation2016]. Sharing synthetic data allows any third party to 1) verify that the published code works, 2) debug the code, and 3) write valid code for alternative analyses. It is important to note that complex multivariate relationships present in the real data are often lost in synthetic data. Thus, findings from the real data might not be replicated in the synthetic data, and findings in the synthetic data *should not be substantively interpreted*. Still, sharing synthetic data facilitates data requests from third parties. A third party can write analysis code based on the synthetic data, and send it to the authors who evaluate it on the real data and send back the results.

@@

* `open_data(data)`: This function stores the `data` object (a `data.frame` or `matrix`) in a spreadsheet file (called `data.csv` by default).
This file should now be (manually) added to the 'Git' repository, committed, and pushed to GitHub.
Once the GitHub repository is made public, these data will be open to the public.
Assume that, once you do this, the data cannot be un-shared.
* `closed_data(data)`: This function also stores the data in a local file (called `data.csv` by default), but that file is added to the `.gitignore` file so it cannot be accidentally added to the 'Git' repository.
The function also adds a checksum for the original data in the `.worcs` project file, and creates a synthetic dataset (called `synthetic_data.csv` by default).
The user should commit all changed files and push them to GitHub.
Once the GitHub repository is made public, people will have access to a checksum for the original data that exist on your local machine, a codebook describing those data, and a synthetic copy of the data.
<!-- Maybe remark that in the "closed" case, a the data should be backupped somewhere else, as GitHub will not do the job in this setting. -->

>>>>

```{r, scholarbib, echo = FALSE, fig.cap="Exporting a BibTex reference from Google Scholar"}
knitr::include_graphics("scholar_bib.png")
```

@@

The second solution is to share a synthetic dataset with similar characteristics
to the real data. Synthetic data mimic the level of measurement and
(conditional) distributions of the real data
[see @nowokSynthpopBespokeCreation2016]. Sharing synthetic data allows any third
party to 1) verify that the published code works, 2) debug the code, and 3)
write valid code for alternative analyses. It is important to note that complex
multivariate relationships present in the real data are often lost in synthetic
data. Thus, findings from the real data might not be replicated in the synthetic
data, and findings in the synthetic data *should not be substantively interpreted*.
Still, sharing synthetic data facilitates data requests from third parties. A
third party can write analysis code based on the synthetic data, and send it to
the authors who evaluate it on the real data and send back the results. The
`worcs` package offers a simple but flexible function for synthetic data,
`synthetic()`, which by default uses random forests to generate a model for
synthesis (see @wrightRangerFastImplementation2015). For data synthesis to work
properly, it is essential that the `class` (data type) of variables is defined
correctly. As of Version `r cran_version()`, numeric, integer, and factor types
are supported out of the box. Other types of variables should be converted to
one of these types, or users can use a custom `model_expression` when calling
`synthetic`.

@@

* `open_data(data)`: This function stores the `data` object (a `data.frame` or `matrix`) in a spreadsheet file (called `data.csv` by default).
This file should now be (manually) added to the 'Git' repository, committed, and pushed to GitHub.
Once the GitHub repository is made public, these data will be open to the public.
Assume that, once you do this, the data cannot be un-shared.
* `closed_data(data)`: This function also stores the data in a local file (called `data.csv` by default), but that file is added to the `.gitignore` file so it cannot be accidentally added to the 'Git' repository.
The function also adds a checksum for the original data in the `.worcs` project file, and creates a synthetic dataset (called `synthetic_data.csv` by default).
The user should commit all changed files and push them to GitHub.
Once the GitHub repository is made public, people will have access to a checksum for the original data that exist on your local machine, a codebook describing those data, and a synthetic copy of the data.

<!-- Maybe remark that in the "closed" case, a the data should be backupped somewhere else, as GitHub will not do the job in this setting. -->
